---
title: "Explanation"
author: "Abhishek"
date: "12/9/2019"
output: html_document
---

Finally, I have added an interactive plot using plotly to explain that when there are more trains and train access to the public, there is 
lesser ownership of cars.

The value '1' represents places with MSA Rail and '2' represents places with no MSA Rail. 


```{r, echo=TRUE, message=FALSE, warning=FALSE}

library(plotly)
library(tidyverse)

  
#Preparing data for plotly interactive plots


data2009 <- year_2009%>%
  dplyr::filter(HHFAMINC %in% c("03","07","09"))%>%
  mutate(Income = factor(HHFAMINC,levels = c("03","07","09"), labels = c("Low","Medium","High")), Rail = case_when(RAIL == "01" ~ "With Rail",
                          RAIL == "02" ~ "Without Rail"))%>%
  group_by(HHFAMINC, Rail)%>%
  summarise(mean_1 = weighted.mean(HHVEHCNT, WTHHFIN), sd(HHVEHCNT))




data2017 <- year_2017%>%
   dplyr::filter(HHFAMINC %in% c("03","07","09"))%>%
  mutate(Income = factor(HHFAMINC,levels = c("03","07","09"), labels = c("Low","Medium","High")), Rail = case_when(RAIL == "01" ~ "With Rail",
                          RAIL == "02" ~ "Without Rail"))%>%
  group_by(HHFAMINC, Rail)%>%
  summarise(mean_1 = weighted.mean(HHVEHCNT, WTHHFIN), sd(HHVEHCNT))
  
```


YEAR 2009


```{r, echo=TRUE, message=FALSE, warning=FALSE}

#Forming and displaying a plot


plot2 <-  ggplot(data2009, aes(x = HHFAMINC)) + 
  geom_col(aes(fill= Rail, y= mean_1) , colour = "black", size = .1, position = "dodge") +
    ggtitle(NULL, NULL) +
    labs(x = "Income Groups", y = "Car ownership") +
    scale_fill_brewer(palette = "PuBuGn", direction = 1) + 
    theme(axis.text.x = element_text(size  = 10, 
                                     angle = 45,
                                     hjust = 1,
                                     vjust = 1))

plot2 %>% ggplotly(tooltip = c("x", "y", "fill")) %>% layout(boxmode = "group")

  

```
  
  
YEAR 2017  
  
``` {r, echo=FALSE, message=FALSE, warning=FALSE}  
  

plot <-  ggplot(data2017, aes(x = HHFAMINC)) + 
  geom_col(aes(fill= Rail, y= mean_1) , colour = "black", size = .1, position = "dodge") +
    ggtitle(NULL, NULL) +
    labs(x = "Income Groups", y = "Car ownership") +
    scale_fill_brewer(palette = "PuBuGn", direction = 1) + 
    theme(axis.text.x = element_text(size  = 10, 
                                     angle = 45,
                                     hjust = 1,
                                     vjust = 1))
  
  
  plot %>% ggplotly(tooltip = c("x", "y", "fill")) %>% layout(boxmode = "group")











```


Now lets see how that varies based on the city, so theres a column in our dataset called MSASIZE which is basically the different categories of cities based on its population. 


From the above Graphs, we can see that there are more cars purchased by not just one but by all three income groups if there is not much access to Rail or if the cities have no MSA Rail.

Thus, we can learn that there is a high need to develop the existing rail infrastructure to bring the accessibility of train rides to all, if not most of the cities.